Include Libraries

```{r}
library (dplyr)
library (tidyverse)
library (ggplot2)
library (ggExtra)
library (ggside)
library (ggforce)
library (gridExtra)
library (patchwork)
library (lubridate)
library (scales)
library (purrr)
library (ggtext)
```

Variables

```{r}
#common variables
teststartload = 1e-2 #10mN
picturewidth = 6 #units in Inches
pictureheight = 4 #units in Inches
bincount = 80 #20 for 5N if bins at quarter newton
savepath = "./Graphs"

colpal <- colorRampPalette(c("red", "orange", "yellow", "green", "blue", "purple"))
shapes_3 <- c(21,24,22)
lines_3 <- c("solid", "dashed", "dotted")
```

Setup

```{r}
sample = "SiC Stats"
undertitle = paste("From", sample, "Testing")
```

Useful Functions

```{r}
reindex <- function(df){
  rownames(df) <- 1:nrow(df)
  return(df)
}
```

Data Reading and Processing

```{r}
filestolist <- function(folderdir,
                        loadstart = 1e-2,
                        plotcount = 20,
                        indent = 1,
                        uniquenames = FALSE) {
  
  directories <- 
    list.files(folderdir, pattern = ".csv$", recursive = TRUE, full.names = TRUE)
  
  filenames <- 
    list.files(folderdir, pattern = ".csv$", recursive = TRUE, full.names = FALSE)
  
  datalist <- 
    lapply(directories, read.csv)
  
  if(!uniquenames) {
    
    names(datalist) <- 
      gsub("\\.csv$", "", filenames)
    
    } else {
      
    names(datalist) <- 
      gsub("\\.csv$", "", gsub("^\\.\\/DataFiles\\/", "", directories))
    
  }
  
  datalistclean <- 
    map(datalist, ~ .x %>% 
          mutate(
            Time..min. = Time..min. - Time..min.[which.max(Load..N.>loadstart)],
            Depth..µm. = Depth..µm. - Depth..µm.[which.max(Load..N.>loadstart)],
            )
        )
  
  datalistclean <- 
    map(datalistclean, ~ .x %>% 
          filter(
            Time..min. > 0,
            Time..min. < Time..min.[which.max(Load..N.)]
            )
        )
  
  selecteddata <- indent:min(plotcount + indent - 1, length(datalistclean))
  
  list(
    name = basename(normalizePath(folderdir)),
    datalist = datalist,
    datalistclean = datalistclean,
    selecteddata = selecteddata
  )
  
}
```

Extrapolate Data

Main Data Conditioning Function

```{r}
dfcond <- function(df, df_clean, source = NA, noiseoff = 0, loadstart = 1e-2) {
  
  idx <- 1:which.max(df[3] > loadstart)
  
  #noise metrics
  AEnoise <- mean(df[idx, 5])
  Noisefloor <- max(df[idx, 5]) + noiseoff
  
  #peak extraction
  peak_idx <- which(df_clean[5] > Noisefloor)
  
  peakheight <- df_clean[peak_idx, 5] - AEnoise
  peakload <- df_clean[peak_idx, 3]
  peakdepth <- df_clean[peak_idx, 2]
  
  #remove duplicates
  dupes <- duplicated(peakheight)
  
  if(any(dupes)){
    peakheight <- peakheight[!dupes]
    peakload <- peakload[!dupes]
    peakdepth <- peakdepth[!dupes]
  }
  
  #recreate indentdf row
  indentrow <- data.frame(
    n_peaks = length(peakheight),
    mean_AE = mean(peakheight),
    total_AE = sum(peakheight),
    first_AE = peakheight[1],
    first_load = peakload[1],
    Source = source
  )
  
  list(
    AEnoise = AEnoise,
    Noisefloor = Noisefloor,
    peakheight = peakheight,
    peakload = peakload,
    peakdepth = peakdepth,
    indentdfrow = indentrow
  )
  
}

makedfcond <- function(df, dfclean, noiseoff, loadstart){
  
  source = lapply(strsplit(names(dfclean), "/"), '[[', 1)
  
  pmap(list(df, dfclean, source), dfcond, noiseoff, loadstart)
}
```

Readjust data considering new values (AEnoise)

```{r}
readjust <- function(df, cond) {
  df %>% 
    mutate(AE_adj = Acoustic..aJ. - cond$AEnoise)
  }
```

Create Peaksdf, contains all peak data

```{r}
#function to create peaksdf
peaksdfrow <- function(df, source = NA){
  
  if(length(df$peakheight) > 0){
    
    dfrow <- data.frame(
      AE = df$peakheight,
      Load = df$peakload,
      Depth = df$peakdepth,
      PeakNumber = 1:length(df$peakheight),
      Source = source)
    
  } else {
    
    dfrow <- data.frame(
      AE = NULL,
      Load = NULL,
      Depth = NULL,
      PeakNumber = NULL,
      Source = NULL)
    }
}

makepeaksdf <- function(dfcond){
  reindex(
    bind_rows(
      map2(dfcond, 
        lapply(strsplit(names(dfcond), "/"), '[[', 1), peaksdfrow)))
}
```

Data Processing Function Calls

```{r}
datamaster <- filestolist(folderdir = "./DataFiles/Sic Stats Final", 
                          loadstart = 1e-1)

datalist <- datamaster[[2]]
datalistclean <- datamaster[[3]]
selecteddata <- datamaster[[4]]

datacond <- makedfcond(datalist, datalistclean, noiseoff = 600, loadstart = 1e-1)

datalistclean <- map2(datalistclean, datacond, readjust)

indentdf <- reindex(do.call(rbind, lapply(datacond, `[[`, "indentdfrow")))

peaksdf <- makepeaksdf(datacond)
```

Do after Main Conditioning Loop

```{r}
#Code which requires extrapolation done in Main Data Conditioning Loop

#find maximum load
loadmax = round(max(datalistclean[[100]][3]))

#find gradations of bins from bincount and maximum load
binloads = ((0:bincount)/bincount)*loadmax

#determine average noise level and noise floor for graphs
AEnoise = mean(sapply(datacond, `[[`, "AEnoise"))
Noisefloor = mean(sapply(datacond, `[[`, "Noisefloor"))
```

Peak Data Stats for Consistency Plot

```{r}
makestats<- function(pdf){
  stats <- na.omit(
    pdf %>% 
  group_by(PeakNumber) %>% 
  summarize(
    sdload = sd(Load),
    sddepth = sd(Depth),
    meanAE = mean(AE),
    meanLoad = mean(Load),
    meanDepth = mean(Depth)))
  
  stats
}

peaknumstats <- makestats(peaksdf)
```

Graph Data

AE vs Depth

```{r}
#Graph AE vs Depth for each indent
ggplot(
  bind_rows(
    datalistclean[selecteddata],
    .id = "Test"), 
  aes(x = Depth..µm., 
      y = AE_adj, 
      colour=Test)) +
  
  geom_path() +
  
  geom_hline(yintercept=Noisefloor, linetype="longdash", col = 'black')+
  
  annotate("text", 
           x = 1, 
           y = Noisefloor, 
           label = "Noise Floor", 
           vjust = -1,
           col = "black") +
  
  scale_y_continuous(labels = scales::number) +
  
  labs(x = "Depth (µm)", 
       y = "Acoustic Energy (aJ)",) +
  
  theme_bw() +
  theme(legend.position = "none")

ggsave(
  paste0(savepath, "/AEDepth/", sample, " Acoustic Energy vs Depth.png"), 
  width = picturewidth, height = pictureheight
  )
```

AE vs Time

```{r}
#Graph AE vs Time for each indent
ggplot(
  bind_rows(
    datalistclean[selecteddata],
    .id = "Test"),
  aes(x = Time..min. * 60, 
      y = AE_adj,
      colour=Test)) +
  
  geom_path() +
  
  geom_hline(yintercept=Noisefloor, linetype="longdash", col = "black")+
  annotate("text", 
           x = max(datalistclean[[1]][1]) * 45, 
           y = Noisefloor, 
           label = "Noise Floor", 
           vjust = -1,
           col = "black") +
  
  
  labs(x = "Time (Sec)", 
       y = "Acoustic Energy (aJ)",) +
  
  scale_y_continuous(labels = scales::number) +
  
  theme_bw() +
  theme(legend.position = "none")

ggsave(
  paste0(savepath, "/AETime/", sample, " Acoustic Energy vs Time.png"), 
  width = picturewidth, height = pictureheight
  )
```

Load vs Depth

```{r}
#Graph Load vs Depth for each indent
ggplot(
  bind_rows(
    datalistclean[selecteddata], 
    .id = "Test"), 
  aes(x = Depth..µm., 
      y = Load..N., 
      colour=Test)) +
  
  labs(x = "Depth (µm)", 
       y = "Load (N)",) +
  
  geom_path() +
  
  scale_y_continuous(limits = c(0, loadmax)) +
  
  theme_bw() +
  theme(legend.position = "none")

ggsave(
  paste0(savepath, "/DepthLoad/", sample,"Load vs Depth.png"), 
  width = picturewidth, height = pictureheight
)
```

AE vs Depth with Load vs Depth

```{r}
#Graph AE vs Depth AND Load vs. Depth on a single indent (determined by plotstart)
#scales second axis properly such that max load and max AE are at same height
plotstart = selecteddata[[1]]

scale =
  (max(datalistclean[[plotstart]][5]) - datacond[[plotstart]]$AEnoise)/
  max(datalistclean[[plotstart]][3])

ggplot() +
  
  geom_path(data = datalistclean[[plotstart]], 
            aes(
              x=Depth..µm., 
              y=Acoustic..aJ.- datacond[[plotstart]]$AEnoise), 
            color = "black") +
  
  geom_path(data = datalistclean[[plotstart]], 
            aes(
              x=Depth..µm., 
              y=Load..N.*scale), 
            color = "red2") +
  
  geom_hline(
    yintercept = 
      datacond[[plotstart]]$Noisefloor - 
      datacond[[plotstart]]$AEnoise, 
    linetype="longdash", 
    col = 'black')+
  
  annotate("text", 
           x = .75, 
           y = datacond[[plotstart]]$Noisefloor - datacond[[plotstart]]$AEnoise, 
           label = "Noise Floor", 
           vjust = -0.75) +
  
  labs(subtitle=paste(undertitle, "Indent", plotstart, sep = " "), 
       x = "Depth (µm)") +
  
  scale_y_continuous(name = "Acoustic Energy (aJ)", 
                     sec.axis = sec_axis(~.*1/scale, name = "Load (N)")) +
  
  coord_cartesian(ylim = c(0,12500)) +
  theme_bw() +
  theme(axis.title.y.right = element_text(color = "red2"))

ggsave(
  paste0(savepath, "/AELoadDepth/", sample, "indent", plotstart, "AELoad Overlay.png"), 
  width = picturewidth, height = pictureheight
)
```

Distribution plot

Dist plot Variables and Aesthetics

```{r}
ymax = 10^(floor(max(log10(peaksdf$AE))))
ymin = min(peaksdf$AE)
xmax = round(loadmax)
xmin = 0
bins = 50
densityscale = 20
transparency = 0.2
groups <- 10
colors <- colpal(groups)
```

Empty Plot for Pasting

```{r}
empty <- ggplot()+
         theme(axis.ticks=element_blank(), 
               panel.background=element_blank(), 
               axis.text.x=element_blank(), axis.text.y=element_blank(),           
               axis.title.x=element_blank(), axis.title.y=element_blank())
```

Consistency Plot

```{r}
statsplot <- ggplot() +
  
  geom_point(data = peaksdf %>% filter(Load <= xmax & PeakNumber <= groups), 
             aes(
               x = Load, 
               y = AE,
               shape = factor(PeakNumber),
               fill = factor(PeakNumber)),
             color = "black",
             alpha = transparency,
             size = 2) +
  
  geom_point(data = peaknumstats %>% filter(PeakNumber <= groups),
             aes(
               x = meanLoad,
               y = meanAE,
               shape = factor(PeakNumber),
               fill = factor(PeakNumber)),
             color = "black",
             size = 3) +
  
  geom_errorbarh(data = peaknumstats %>% filter(PeakNumber <= groups),
                aes(
                  y = meanAE,
                  xmin = meanLoad - sdload,
                  xmax = meanLoad + sdload,
                )) +
  
  scale_shape_manual(name = paste0("Peak", "\n", "Number"), values = rep(shapes_3, length.out = groups)) +
  scale_fill_manual(name = paste0("Peak", "\n", "Number"), values = colors) +
  scale_color_manual(name = paste0("Peak", "\n", "Number"), values = colors) +
  
  labs(x = "Load (N)", 
       y = "Acoustic Energy (aJ)") +

  coord_cartesian(xlim = c(xmin, xmax), ylim = c(ymin, ymax)) +
  
  scale_y_continuous(trans = "log10", labels = scales::label_log()) +
  
  theme_bw()

ggsave(
  paste0(savepath,"/firstpeaksplot/", sample, " First Peaks Average.png"), 
  width = picturewidth, height = pictureheight
)

statsplot
```

X (load) distribution plot

```{r}
xdistributioncolor <- ggplot() +
  
  # geom_histogram(data = peaksdf %>% filter(Load <= xmax & PeakNumber <= groups),
  #                aes(
  #                  x = Load,
  #                  fill = factor(PeakNumber)),
  #                alpha = 0.5,
  #                bins = bins) +
  
  geom_histogram(data = peaksdf %>% filter(Load <= xmax & PeakNumber <= groups),
                 aes(
                   x = Load),
                   fill = "darkgrey",
                 alpha = 0.5,
                 bins = bins) +
  
  geom_density(data = peaksdf %>% filter(Load <= xmax & PeakNumber <= groups),
               aes(
                 x = Load,
                 y = after_stat(scaled) * densityscale,
#                 linetype = factor(PeakNumber),
                 color = factor(PeakNumber))) +
  
  coord_cartesian(xlim = c(xmin, xmax))+
  
  labs(x = "Load (N)", 
       y = "Count / Density") +
  
#  scale_linetype_manual(name = "Legend", values = rep(lines_3, length.out = groups)) +
  scale_fill_manual(name = "Legend", values = colors) +
  scale_color_manual(name = "Legend", values = colors) +
    
  theme_bw()

ggsave(
  paste0(savepath,"/distribution/", sample, " Load distribution colored.png"), 
  width = picturewidth, height = pictureheight
)

xdistributioncolor
```

Y (AE) distribution plot

```{r}
ydistribution <- ggplot() +
  
  geom_histogram(data = peaksdf %>% filter(Load <= xmax & PeakNumber <= groups & AE <= ymax),
                 aes(x = AE),
                 bins = bins,
                 fill = "darkgrey",
                 alpha = 0.5) +
  
  # geom_histogram(data = peaksdf %>% filter(Load <= xmax & PeakNumber <= groups),
  #                aes(x = AE,
  #                    fill = factor(PeakNumber)),
  #                bins = bins,
  #                alpha = 0.5) +
  # 
  # scale_fill_manual(name = "Legend", values = colors) +
  
  # scale_x_continuous(labels = scales::label_log()) +
  
  coord_cartesian(xlim = c(ymin, ymax)) +
  
  labs(x = "Acoustic Energy (aJ)", 
       y = "Count") +
  
  theme_bw()

ggsave(
  paste0(savepath,"/distribution/", sample, " AE distribution.png"), 
  width = picturewidth, height = pictureheight
)

ydistribution
```

Final Plot with Margins

```{r}
statsplotmodified <- statsplot + 
  
  scale_y_continuous(trans='log10', 
                     labels = scales::label_log()) +
  
  theme(legend.position = "bottom", 
        plot.title = element_blank(), 
        plot.subtitle = element_blank())

xdistributionmodified <- xdistributioncolor + 
  
  theme_void() + 
  
  theme(legend.position = "none", 
        plot.title = element_blank(), 
        panel.background = element_rect(fill = "white"),
        plot.background  = element_rect(fill = "white"),
        plot.subtitle = element_blank(), 
        plot.margin = unit(c(0, 0, 0, 0.4), "in"))


ydistributionmodified <- ydistribution + 
  
  scale_x_continuous(trans='log10')+
  
  coord_flip() + 
  
  theme_void() + 
  
  theme(plot.title = element_blank(), 
        plot.subtitle = element_blank(),
        panel.background = element_rect(fill = "white"),
        plot.background  = element_rect(fill = "white"),
        plot.margin = unit(c(0, 0, 1.3, 0), "in"))


distfinal <- arrangeGrob(
  xdistributionmodified,    # Top marginal plot (x-axis)
  empty,          # Empty cell for spacing
  statsplotmodified,        # Main scatterplot
  ydistributionmodified,    # Right marginal plot (y-axis)
  ncol = 2,      # Arrange in 2 columns
  widths = c(4, 1), # Relative widths of columns (main plot wider)
  heights = c(2, 3) # Relative heights of rows (main plot taller)
)

ggsave(
  paste0(savepath,"/distribution/", sample, " Final distribution.png"), 
  width = 8, height = 8, distfinal
  )
```

Crack Correlation

Read CSV file that contains crack lengths and acoustic energy

```{r}
cracklengths <- read.csv("./DataFiles/Crack Correlation/Surface Crack Lengths.csv")
hardness <- read.csv("./DataFiles/Hardness/hardness correlation.csv")
```

Create Plot of AE vs Crack Length

```{r}
fitmodel <- lm(log(Acoustic.Energy) ~ log(Crack.Length), data = cracklengths)

a_pl = exp(coef(fitmodel)[1])
b_pl = coef(fitmodel)[2]
r2_pl <- summary(fitmodel)$r.squared

label_pl <- paste0(
  "y = ", round(a_pl, 4), 
  " * x^", round(b_pl, 4), 
  "\nR² = ", round(r2_pl, 4))

ggplot(data = cracklengths,
       aes(x = Crack.Length,
           y = Acoustic.Energy)) +
  
  geom_point() +
  
  stat_function(fun = function(x) a_pl * x ** b_pl,
                linetype = "dashed",
                linewidth = 1,
                color = "red4") +
  
  annotate("text", 
           x = max(cracklengths$Crack.Length) * 0.7, 
           y = max(cracklengths$Acoustic.Energy) * 0.005, 
           label = label_pl, hjust = 0.5, size = 5,
           color = "black") +
  
  scale_y_continuous(trans = 'log10', labels = scales::label_log()) +
  scale_x_continuous(trans = 'log10') +
  
  labs(y = "Acoustic Energy (aJ)",
       x = "Crack Length (µm)") +
  
  theme_bw()

ggsave(
  paste0(savepath,"/correlation/Correlation Fit.png"), 
  width = picturewidth, height = pictureheight
)
```

Create Predictive Interval

```{r}
pimodel <- lm(log(Crack.Length) ~ log(Acoustic.Energy), data = cracklengths)

a_pi = exp(coef(pimodel)[1])
b_pi = coef(pimodel)[2]
r2_pi <- summary(pimodel)$r.squared

label_pi <- paste0(
  "y = ", round(a_pi, 4), 
  " * x^", round(b_pi, 4), 
  "\nR² = ", round(r2_pi, 4))

prediction <- exp(predict(pimodel, interval = "prediction"))

SSAE = c(7160, 4170, 1e5)
SSCL = c(54.0, 89.6)

SSPI <- exp(predict(pimodel, newdata = data.frame(Acoustic.Energy = SSAE), interval = "prediction"))


ggplot() +
  
  geom_point(data = cracklengths, aes(y = Crack.Length, x = Acoustic.Energy)) +
  
  geom_line(data = cbind(prediction,cracklengths), aes(x = Acoustic.Energy, y = upr), linetype = "longdash", color = "red4") +
  geom_line(data = cbind(prediction,cracklengths), aes(x = Acoustic.Energy, y = fit)) +
  geom_line(data = cbind(prediction,cracklengths), aes(x = Acoustic.Energy, y = lwr), linetype = "longdash", color = "red4") +
  
  # geom_segment(data = SSPI, aes(x = SSAE[1],
  #                               xend = SSAE[1],
  #                               y = SSPI[1,2],
  #                               yend = SSPI[1,3]),
  #              color = "green4") +
  # 
  # geom_point(data = cbind(SSAE, SSCL),
  #            aes(x = SSAE[1],
  #                y = SSCL[1]),
  #            color = "green4",
  #            size = 3) +
  # 
  # annotate("text",
  #          x = SSAE[1] + 3000,
  #          y = SSPI[1,2] - 7,
  #          label = "Sample 1",
  #          color = "green4") +
  # 
  # geom_segment(data = SSPI, aes(x = SSAE[2],
  #                               xend = SSAE[2],
  #                               y = SSPI[2,2],
  #                               yend = SSPI[2,3]),
  #              color = "blue") +
  # 
  # geom_point(data = cbind(SSAE, SSCL),
  #            aes(x = SSAE[2],
  #                y = SSCL[2]),
  #            color = "blue",
  #            size = 3) +
  # 
  # annotate("text",
  #          x = SSAE[2]+1000,
  #          y = SSPI[2,3] + 30,
  #          label = "Sample 2",
  #          color = "blue") +
  # 
  # geom_segment(data = SSPI, aes(x = SSAE[3],
  #                               xend = SSAE[3],
  #                               y = SSPI[3,2],
  #                               yend = SSPI[3,3]),
  #            color = "red") +
  # 
  # annotate("text",
  #          x = SSAE[3] + 75000,
  #          y = SSPI[3,2] - 15,
  #          label = "Example",
  #          color = "red") +
  
  # annotate("text", 
  #        y = max(cracklengths$Crack.Length) * 0.7, 
  #        x = max(cracklengths$Acoustic.Energy) * 0.005, 
  #        label = label_pi, hjust = 0.5, size = 5,
  #        color = "black") +
  
  scale_x_continuous(trans = "log10", labels = scales::label_log()) +
  scale_y_continuous(trans = "log10") +
  
  labs(y = "Crack Length d (µm)", 
       x = "Acoustic Energy (aJ)") +
  
  theme_bw()

ggsave(
  paste0(savepath,"/correlation/Correlation PI 3.png"), 
  width = picturewidth, height = pictureheight
)
```

Functions for Predictive Index

PI Function

```{r}
Pindex <- function(data, 
                   x, 
                   y, 
                   fittype = "power",
                   xlab = "X Label", 
                   ylab = "Y Label",
                   xlinear = FALSE,
                   ylinear = TRUE,
                   xlablog = TRUE,
                   ylablog = TRUE,
                   annolow = TRUE) 
  {
  
  xname <- deparse(substitute(x))
  yname <- deparse(substitute(y))
  
  xrange = range(data[[xname]])
  yrange = range(data[[yname]])
  
  points = data.frame(seq(xrange[1], xrange[2], length.out = 1000))
  names(points) <- xname
  
  curve <- switch(fittype,
                  "exp" = {
                    
                    tempmodel <- lm(
                      reformulate(xname,
                                  paste0("log(", yname, ")")),
                      data = data
                    )
                    
                    tempprediction <- exp(predict(tempmodel, 
                                                  newdata = points, 
                                                  interval = "prediction")
                    )
                    
                    a <- exp(coef(tempmodel)[1])
                    b <- coef(tempmodel)[2]
                    r2 <- summary(tempmodel)$r.squared
                    
                    label <- paste0(
                      "y = ", round(a, 4),
                      " * e^", round(b, 4),
                      " * x",
                      "\nR² = ", round(r2, 4))
                    
                  },
                  
                  "linear" = {
                    
                    tempmodel <- lm(
                      reformulate(xname, yname),
                      data = data
                    )
                    
                    tempprediction <- predict(tempmodel, 
                                              newdata = points, 
                                              interval = "prediction")
                    
                    a <- coef(tempmodel)[2]
                    b <- coef(tempmodel)[1]
                    r2 <- summary(tempmodel)$r.squared
                    
                    label <- paste0(
                      "y = ", round(a, 4),
                      " * x + ", round(b, 4),
                      "\nR² = ", round(r2, 4))
                    
                  },
                  
                  "power" = {
                    
                    tempmodel <- lm(
                      reformulate(paste0("log(", xname, ")"),
                                  paste0("log(", yname, ")")),
                      data = data
                    )
                    
                    tempprediction <- exp(predict(tempmodel, 
                                                  newdata = points, 
                                                  interval = "prediction")
                    )
                    
                    a <- exp(coef(tempmodel)[1])
                    b <- coef(tempmodel)[2]
                    r2 <- summary(tempmodel)$r.squared
                    
                    label <- paste0(
                      "y = ", round(a, 4),
                      " * x^", round(b, 4),
                      "\nR² = ", round(r2, 4))
                    
                  }
                  
                  )

  
  if(annolow) {labscale = 1/4} else {labscale = 3/4}
  
  if(xlinear){
    xlabelpos <- 13 * ((xrange[2] - xrange[1]) / 16) + xrange[1]
  } else {
    xlabelpos <- 10 ** ((13 * (log10(xrange[2]) - log10(xrange[1])) / 16) + log10(xrange[1]))
  }

  if(ylinear){
    ylabelpos <- labscale * (yrange[2] - yrange[1]) + yrange[1]
  } else {
    ylabelpos <- 10 ** (labscale * (log10(yrange[2]) - log10(yrange[1])) + log10(yrange[1]))
  }
  
  fitpoints = cbind(points, tempprediction)
  
  p <- ggplot() +
    
    geom_point(data = data, aes(x = {{x}}, y = {{y}})) +
    
    geom_line(data = fitpoints, aes(x = {{x}}, y = upr), linetype = "longdash", color = "red4") +
    
    geom_line(data = fitpoints, aes(x = {{x}}, y = fit), linetype = "longdash", color = "black") +
    
    geom_line(data = fitpoints, aes(x = {{x}}, y = lwr), linetype = "longdash", color = "red4") +
    
    annotate("text", x = xlabelpos, y = ylabelpos, label = label, 
             hjust = 0.5, vjust = 0.5, size = 5, color = "black") +
    
    labs(x = xlab, y = ylab) +
    
    theme_bw()
  
  
    
  if (xlablog && !xlinear) {
    p <- p +
      scale_x_continuous(trans = "log10", label = scales::label_log())
    
  } else if(!xlinear){
    p <- p +
      scale_x_continuous(trans = "log10")
  }
  
  if (ylablog && !ylinear) {
    p <- p +
      scale_y_continuous(trans = "log10", label = scales::label_log())
    
  } else if(!ylinear){
    p <- p +
      scale_y_continuous(trans = "log10")
  }
  
  
  
  ggsave(
    paste0(savepath,"/intervals/", xname, "-", yname, ".png"),
    width = picturewidth, height = pictureheight
  )
  
  p
  
}
```

Precision of Interval Function

```{r}
PIprecision <- function(data = hardness, 
                        x = Acoustic.Energy, 
                        y = Hardness,
                        xlab = "X Label",
                        linear = FALSE,
                        lablog = TRUE) 
  {
  
  xname <- deparse(substitute(x))
  yname <- deparse(substitute(y))
  
  logpoints = 10^(seq(log10(min(data[[xname]])),log10(max(data[[xname]])), by = 0.01))

  tempmodel <- lm(
    reformulate(paste0("log(", xname, ")"),
                paste0("log(", yname, ")")),
    data = data
  )
  
  newdata <- setNames(
    data.frame(logpoints),
    xname
  )

  tempprediction <- exp(
    predict(tempmodel, 
            newdata, 
            interval = "prediction")
  )
  
  tempinterval <- as.data.frame(tempprediction) %>% mutate(deltad = (upr-lwr)/fit)
  
  p <- ggplot(data = cbind(tempinterval,logpoints),
         aes(
           x = logpoints,
           y = deltad)) +
    
    geom_path() +
    
    scale_y_continuous(label = scales::percent) +
    
    labs(y = "∆d / d fit", x = xlab) +
    
    theme_bw()
  
  if (lablog && !linear) {
    p <- p +
      scale_x_continuous(trans = "log10", label = scales::label_log())
    
  } else if(!linear){
    p <- p +
      scale_x_continuous(trans = "log10")
  }
  
    ggsave(
      paste0(savepath,"/interval precision/", xname, "-", yname, ".png"),
      width = picturewidth, height = pictureheight
      )
    
    p
}
```

PI Analysis, assuming various fits

X = AE

```{r}
Pindex(data = hardness, 
       x = Acoustic.Energy, 
       y = Hardness, 
       fittype = "power",
       xlab = "Acoustic Energy (aJ)", 
       ylab = "Hardness (GPa)",
       xlinear = FALSE,
       xlablog = TRUE,
       ylinear = TRUE,
       ylablog = FALSE,
       annolow = FALSE)

PIprecision(hardness, 
            Acoustic.Energy, 
            Hardness, 
            "Acoustic Energy (aJ)",
            linear = FALSE,
            lablog = TRUE)
```

```{r}
Pindex(data = hardness, 
       x = Acoustic.Energy, 
       y = Crack.Length, 
       fittype = "power",
       xlab = "Acoustic Energy (aJ)", 
       ylab = "Crack Length (µm)", 
       xlinear = FALSE,
       xlablog = TRUE,
       ylinear = FALSE, 
       ylablog = FALSE,
       annolow = TRUE)

PIprecision(hardness, 
            Acoustic.Energy, 
            Crack.Length, 
            "Acoustic Energy (aJ)",
            linear = FALSE,
            lablog = TRUE)
```

```{r}
Pindex(data = hardness, 
       x = Acoustic.Energy, 
       y = Load, 
       fittype = "power",
       xlab = "Acoustic Energy (aJ)", 
       ylab = "Load (N)", 
       xlinear = FALSE,
       xlablog = TRUE,
       ylinear = FALSE, 
       ylablog = FALSE,
       annolow = TRUE)

PIprecision(hardness, 
            Acoustic.Energy, 
            Load, 
            "Acoustic Energy (aJ)",
            linear = FALSE,
            lablog = TRUE)
```

X = Hardness

```{r}
Pindex(data = hardness, 
       x = Hardness, 
       y = Acoustic.Energy, 
       fittype = "power",
       xlab = "Hardness (GPa)", 
       ylab = "Acoustic Energy (aJ)", 
       xlinear = TRUE, 
       xlablog = FALSE,
       ylinear = FALSE,
       ylablog = TRUE,
       annolow = FALSE)

PIprecision(hardness, 
            Hardness, 
            Acoustic.Energy, 
            "Hardness (GPa)", 
            linear = TRUE,
            lablog = FALSE) 
```

```{r}
Pindex(data = hardness, 
       x = Hardness, 
       y = Crack.Length, 
       fittype = "power",
       xlab = "Hardness (GPa)",
       ylab = "Crack Length (µm)", 
       xlinear = TRUE,
       xlablog = FALSE,
       ylinear = FALSE,
       ylablog = FALSE,
       annolow = FALSE)

PIprecision(hardness, 
            Hardness, 
            Crack.Length, 
            "Hardness (GPa)", 
            linear = TRUE,
            lablog = FALSE) 
```

```{r}
Pindex(data = hardness, 
       x = Hardness, 
       y = Load,
       fittype = "power",
       xlab = "Hardness (GPa)", 
       ylab = "Load (N)", 
       xlinear = TRUE,
       xlablog = FALSE,
       ylinear = FALSE, 
       ylablog = FALSE,
       annolow = FALSE)

PIprecision(hardness, 
            Hardness, 
            Load, 
            "Hardness (GPa)", 
            linear = TRUE,
            lablog = FALSE) 
```

X = Crack Length

```{r}
Pindex(data = hardness, 
       x = Crack.Length, 
       y= Hardness, 
       fittype = "power",
       xlab = "Crack Length (µm)", 
       ylab = "Hardness (GPa)", 
       xlinear = FALSE, 
       xlablog = FALSE,
       ylinear = FALSE,
       ylablog = FALSE,
       annolow = FALSE)

PIprecision(hardness, 
            Crack.Length, 
            Hardness, 
            "Crack Length (µm)", 
            linear = FALSE,
            lablog = FALSE)
```

```{r}
Pindex(data = hardness, 
       x = Crack.Length,
       y = Acoustic.Energy, 
       fittype = "power",
       xlab = "Crack Length (µm)", 
       ylab = "Acoustic Energy (aJ)", 
       xlinear = FALSE, 
       xlablog = FALSE, 
       ylinear = FALSE,
       ylablog = TRUE,
       annolow = TRUE)

PIprecision(hardness, 
            Crack.Length, 
            Acoustic.Energy, 
            "Crack Length (µm)", 
            linear = FALSE,
            lablog = FALSE)
```

```{r}
Pindex(data = hardness, 
       x = Crack.Length,
       y = Load, 
       fittype = "power",
       xlab = "Crack Length (µm)", 
       ylab = "Load (N)", 
       xlinear = TRUE, 
       xlablog = FALSE, 
       ylinear = TRUE,
       ylablog = FALSE,
       annolow = TRUE)

PIprecision(hardness, 
            Crack.Length, 
            Load, 
            "Crack Length (µm)", 
            linear = TRUE,
            lablog = FALSE)
```

X = Load

```{r}
Pindex(data = hardness, 
       x = Load,
       y = Acoustic.Energy, 
       fittype = "power",
       xlab = "Load (N)", 
       ylab = "Acoustic Energy (aJ)", 
       xlinear = TRUE, 
       xlablog = FALSE, 
       ylinear = FALSE,
       ylablog = TRUE,
       annolow = TRUE)

PIprecision(hardness, 
            Load, 
            Acoustic.Energy, 
            "Load (N)", 
            linear = TRUE,
            lablog = FALSE)
```

```{r}
Pindex(data = hardness, 
       x = Load,
       y = Crack.Length, 
       fittype = "power",
       xlab = "Load (N)", 
       ylab = "Crack Length (µm)", 
       xlinear = TRUE, 
       xlablog = FALSE, 
       ylinear = FALSE,
       ylablog = FALSE,
       annolow = TRUE)

PIprecision(hardness, 
            Load, 
            Crack.Length, 
            "Load (N)", 
            linear = TRUE,
            lablog = FALSE)
```

```{r}
Pindex(data = hardness, 
       x = Load,
       y = Hardness, 
       fittype = "power",
       xlab = "Load (N)", 
       ylab = "Hardness (GPa)", 
       xlinear = TRUE, 
       xlablog = FALSE, 
       ylinear = TRUE,
       ylablog = FALSE,
       annolow = FALSE)

PIprecision(hardness, 
            Load, 
            Hardness, 
            "Load (N)", 
            linear = TRUE,
            lablog = FALSE)
```

Hardness Analysis

Indent Size Effect Demonstration

```{r}
hardness <- read.csv("./DataFiles/Hardness/hardness correlation.csv")

avehard <- hardness %>% group_by(Load) %>% summarize(mean = mean(Hardness))

ggplot() +
  
  geom_point(data = hardness, 
             aes(
               x = Load, 
               y = Hardness)) +
  
  geom_line(data = avehard, 
            aes(
              x = Load, 
              y = mean), 
            color = "red4") +
  
  geom_point(data = avehard, 
             aes(
               x = Load, 
               y = mean), 
             color = "red4", 
             size = 3) +
  
  labs(y = "Hardness (GPa)", 
       x = "Load (N)") +
  
  theme_bw()

ggsave(
  paste0(savepath,"/hardness/indentsizeeffect.png"), 
  width = picturewidth, height = pictureheight
)
```

Serial Sectioning

Generate and Condition Data

```{r}
SSnoiseoffset = 200 #in aJ

SSdatamaster <- filestolist(folderdir = c("./DataFiles/4 Peak 2", "./DataFiles/5 Peak 2"),
                            loadstart = teststartload, 
                            plotcount = 100, 
                            indent = 1,
                            uniquenames = TRUE)

SSdatalist <- SSdatamaster[[2]]
SSdatalistclean <- SSdatamaster[[3]]
SSselecteddata <- SSdatamaster[[4]]

SSdatacond <- makedfcond(SSdatalist, SSdatalistclean, noiseoff = SSnoiseoffset, loadstart = teststartload)

SSdatalistclean <- map2(SSdatalistclean, SSdatacond, readjust)

SSindentdf <- reindex(do.call(rbind, lapply(SSdatacond, `[[`, "indentdfrow")))

SSpeaksdf <- makepeaksdf(SSdatacond)
```

Graph Data

```{r}
plotlist = names(SSdatalistclean)#c("4 Peak 2/Test 1", "4 Peak 2/Test 5")


#scales second axis properly such that max load and max AE are at same height
scale = 
  (vapply(SSdatalistclean[plotlist], function(df) max(df[[5]]), numeric(1)) -
  vapply(SSdatacond[plotlist], function(df) df$AEnoise, numeric(1))) /
  vapply(SSdatalistclean[plotlist], function(df) max(df[[3]]), numeric(1))

walk(plotlist, function(indent) {
  
  p <- ggplot() +
    
    geom_path(data = SSdatalistclean[[indent]],
              aes(
                x = Depth..µm.,
                y = Acoustic..aJ. - SSdatacond[[indent]]$AEnoise),
              color = "black") +
    
    geom_path(data = SSdatalistclean[[indent]], 
              aes(
                x=Depth..µm., 
                y=Load..N. * scale[[indent]]), 
              color = "red2") +
    
    geom_hline(
      yintercept = 
        SSdatacond[[indent]]$Noisefloor - 
        SSdatacond[[indent]]$AEnoise, 
      linetype="longdash", 
      col = 'black')+
  
    annotate("text", 
             x = .75, 
             y = SSdatacond[[indent]]$Noisefloor - SSdatacond[[indent]]$AEnoise, 
             label = "Noise Floor", 
             vjust = -0.75) +
    
    coord_cartesian(ylim = c(0, NA)) +
    
    scale_y_continuous(name = "Acoustic Energy (aJ)", 
                       sec.axis = sec_axis(~. * 1 / scale[[indent]], name = "Load (N)")) +
    
    labs(x = "Depth (µm)") +
    
    theme_bw() +
    theme(axis.title.y.right = element_text(color = "red2"))
  
  ggsave(
    paste0(savepath, "/serialsection/",indent," AELoad Overlay.png"), 
    plot = p,
    width = picturewidth, height = pictureheight
  )
}
)
```

Alumina Testing

```{r}
ALnoiseoffset = 200 #in aJ

ALdatamaster <- filestolist(folderdir = c("./DataFiles/Alumina 5N 5Nmin", "./DataFiles/Alumina 5N 20Nmin", "./DataFiles/Alumina 20N 5Nmin", "./DataFiles/Alumina 20N 20Nmin"),
                            loadstart = teststartload, 
                            plotcount = 100, 
                            indent = 1,
                            uniquenames = TRUE)

ALdatalist <- ALdatamaster[[2]]
ALdatalistclean <- ALdatamaster[[3]]
ALselecteddata <- ALdatamaster[[4]]

ALdatacond <- makedfcond(ALdatalist, ALdatalistclean, noiseoff = ALnoiseoffset, loadstart = teststartload)

ALdatalistclean <- map2(ALdatalistclean, ALdatacond, readjust)

ALindentdf <- reindex(do.call(rbind, lapply(ALdatacond, `[[`, "indentdfrow")))

ALpeaksdf <- makepeaksdf(ALdatacond)

ALlegend = c("20N at 20N/min", "20N at 5N/min", "5N at 20N/min", "5N at 5N/min")
names(ALlegend) <- unique(ALpeaksdf$Source)
```

```{r}
ggplot(ALpeaksdf) +
  geom_histogram(aes(x = Load), fill = "darkgrey", binwidth = 0.25) +
  geom_density(aes(x = Load, y = after_stat(scaled) * 10)) +
  facet_wrap(~ Source, scales = "free", labeller = as_labeller(ALlegend)) +
  labs(x = "Load (N)", 
       y = "Count") +
  theme_bw()

ggsave(
  paste0(savepath,"/ALdistribution/", sample, " Load distribution.png"), 
  width = picturewidth, height = pictureheight
)
```

```{r}
ggplot(ALpeaksdf) +
  geom_histogram(aes(x = Depth), fill = "darkgrey", binwidth = 0.25) +
  geom_density(aes(x = Depth, y = after_stat(scaled) * 15)) +
  facet_wrap(~ Source, scales = "free", labeller = as_labeller(ALlegend)) +
  labs(x = "Depth (μm)", 
       y = "Count") +
  theme_bw()

ggsave(
  paste0(savepath,"/ALdistribution/", sample, " Depth distribution.png"), 
  width = picturewidth, height = pictureheight
)
```

```{r}
ALgroups = 20
ALtransparency = 0.2
ALcolors = colpal(ALgroups)

split_df <- split(ALpeaksdf, ALpeaksdf$Source)

ALstatslist <- do.call(
  rbind,
  Map(
    function(df, src) {
      out <- makestats(df)
      out$Source <- src
      out
    },
    split_df,
    names(split_df)
  )
)



ggplot() +
  
  geom_point(data = ALpeaksdf %>% filter(PeakNumber <= ALgroups), 
             aes(
               x = Load, 
               y = AE,
               shape = factor(PeakNumber),
               fill = factor(PeakNumber)),
             color = "black",
             alpha = ALtransparency,
             size = 2) +

  geom_point(data = ALstatslist %>% filter(PeakNumber <= ALgroups),
             aes(
               x = meanLoad,
               y = meanAE,
               shape = factor(PeakNumber),
               fill = factor(PeakNumber)),
             color = "black",
             size = 3) +

  geom_errorbarh(data = ALstatslist %>% filter(PeakNumber <= ALgroups),
                aes(
                  y = meanAE,
                  xmin = meanLoad - sdload,
                  xmax = meanLoad + sdload,
                )) +

  scale_shape_manual(name = paste0("Peak", "\n", "Number"), values = rep(shapes_3, length.out = ALgroups)) +
  scale_fill_manual(name = paste0("Peak", "\n", "Number"), values = ALcolors) +
  
  facet_wrap(~ Source, scales = "free", labeller = as_labeller(ALlegend)) +

  labs(x = "Load (N)",
       y = "Acoustic Energy (aJ)") +
  # 
  # coord_cartesian(xlim = c(xmin, xmax), ylim = c(ymin, ymax)) +

  scale_y_continuous(trans = "log10", labels = scales::number) +
  
  theme_bw()

ggsave(
  paste0(savepath,"/ALfirstpeaksplot/", sample, " First Peaks Average.png"), 
  width = picturewidth, height = pictureheight
)
```

```{r}
ALsourcenum = length(unique(ALpeaksdf$Source))
ALtransparency2 = 0.25
ALcolors2 = colpal(ALsourcenum)

ALoptimstats <- ALpeaksdf %>% 
  group_by(Source) %>% 
  summarize(meanload = mean(Load), 
            meandepth = mean(Depth), 
            meanAE = mean(AE))

ggplot() +
  
  geom_point(data = ALpeaksdf,
             aes(
               x = Load,
               y = AE,
               shape = factor(Source),
               fill = factor(Source)),
             color = "black",
             alpha = ALtransparency2,
             size = 2) +
  
  geom_point(data = ALoptimstats,
             aes(
               x = meanload,
               y = meanAE,
               shape = factor(Source),
               fill = factor(Source)),
             size = 4) +
  
  geom_mark_rect(data = ALpeaksdf,
                 aes(
                   x = Load,
                   y = AE,
                   fill = factor(Source),
                   color = factor(Source)),
                 alpha = ALtransparency2/4, 
                 radius = 0, 
                 expand = 0.02) +

  scale_shape_manual(name = "Source", values = rep(shapes_3, length.out = ALsourcenum), labels = ALlegend) +
  scale_fill_manual(name = "Source", values = ALcolors2, labels = ALlegend) +
  scale_color_manual(name = "Source", values = ALcolors2, labels = ALlegend) +

  labs(x = "Load (N)",
       y = "Acoustic Energy (aJ)") +
  # 
  # coord_cartesian(xlim = c(xmin, xmax), ylim = c(ymin, ymax)) +

  scale_y_continuous(trans = "log10", labels = scales::number) +
  
  theme_bw()

ggsave(
  paste0(savepath,"/ALfirstpeaksplot/", sample, " First Peaks Average 2.png"), 
  width = picturewidth, height = pictureheight
)



ggplot() +
  
  geom_point(data = ALpeaksdf,
             aes(
               x = Depth,
               y = AE,
               shape = factor(Source),
               fill = factor(Source)),
             color = "black",
             alpha = ALtransparency2,
             size = 2) +
               
  geom_point(data = ALoptimstats,
             aes(
               x = meandepth,
               y = meanAE,
               shape = factor(Source),
               fill = factor(Source)),
             size = 4) +
  
  geom_mark_rect(data = ALpeaksdf,
                 aes(
                   x = Depth,
                   y = AE,
                   fill = factor(Source),
                   color = factor(Source)),
                 alpha = ALtransparency2/4, 
                 radius = 0, 
                 expand = 0.02) +

  scale_shape_manual(name = "Source", values = rep(shapes_3, length.out = ALsourcenum), labels = ALlegend) +
  scale_fill_manual(name = "Source", values = ALcolors2, labels = ALlegend) +
  scale_color_manual(name = "Source", values = ALcolors2, labels = ALlegend) +

  labs(x = "Depth (μm)",
       y = "Acoustic Energy (aJ)") +
  # 
  # coord_cartesian(xlim = c(xmin, xmax), ylim = c(ymin, ymax)) +

  scale_y_continuous(trans = "log10", labels = scales::number) +
  
  theme_bw()

ggsave(
  paste0(savepath,"/ALfirstpeaksplot/", sample, " First Peaks Average 2 Depth.png"), 
  width = picturewidth, height = pictureheight
)
```

Sensor Placement

```{r}
posnoiseoffset = 100 #in aJ

posdatamaster <- filestolist(folderdir = c("./DataFiles/New Sensor Testing", "./DataFiles/Under Sensor No Puck", "./DataFiles/Under Sensor Puck"),
                            loadstart = teststartload, 
                            plotcount = 100, 
                            indent = 1,
                            uniquenames = TRUE)

posdatalist <- posdatamaster[[2]]
posdatalistclean <- posdatamaster[[3]]
posselecteddata <- posdatamaster[[4]]

posdatacond <- makedfcond(posdatalist, posdatalistclean, noiseoff = posnoiseoffset, loadstart = teststartload)

posdatalistclean <- map2(posdatalistclean, posdatacond, readjust)

posindentdf <- reindex(do.call(rbind, lapply(posdatacond, `[[`, "indentdfrow")))

pospeaksdf <- makepeaksdf(posdatacond)
```

```{r}
plotlist = names(posdatalistclean)#c("4 Peak 2/Test 1", "4 Peak 2/Test 5")

walk(plotlist, function(indent) {
  
  p <- ggplot() +
    
    geom_path(data = posdatalistclean[[indent]],
              aes(
                x = Load..N.,
                y = Acoustic..aJ. - posdatacond[[indent]]$AEnoise),
              color = "black") +
    
    geom_hline(
      yintercept = 
        posdatacond[[indent]]$Noisefloor - 
        posdatacond[[indent]]$AEnoise, 
      linetype="longdash", 
      col = 'black')+
  
    annotate("text", 
             x = .75, 
             y = posdatacond[[indent]]$Noisefloor - posdatacond[[indent]]$AEnoise, 
             label = "Noise Floor", 
             vjust = -0.75) +
    
    coord_cartesian(ylim = c(0, NA)) +
    
    labs(x = "Load (N)", y = "Acoustic Energy (aJ)") +
    
    theme_bw()
  
  ggsave(
    paste0(savepath, "/sensorposition/",indent," AELoad Overlay.png"), 
    plot = p,
    width = picturewidth, height = pictureheight)
  }
  )
```

```{r}
possummary <- aggregate(posindentdf$first_load, list(posindentdf$Source), mean)
```

Export Data

```{r}
exportcsv <- function(df){
  write.csv(df, paste0("Export/",deparse(substitute(df)),".csv"), row.names = FALSE)
  }
```

```{r}
exportcsv(ALindentdf)
exportcsv(SSindentdf)
exportcsv(indentdf)

exportcsv(ALpeaksdf)
exportcsv(SSpeaksdf)
exportcsv(peaksdf)
```
